Spatial Reasoning and Statistical Graphics

### 2014-11-20 Paper/Draft1/TestingVisualAptitude.Rnw
Spacing of newtext boxes

\newtext{Figure \ref{fig:lineuptaskmatrix} shows the correlations between the three lineup tasks and the figure classification, card rotation, and paper folding tasks. The visual search task was only slightly correlated with the three lineup tasks and has been omitted from this figure. Performance on lineup tasks 1 and 2, which dealt with the distributuion of two groups of numerical data, is most strongly correlated with the performance on the figure classification task, which measures general reasoning ability. Performance on lineup task 3, which dealt with the identification of nonnormal residual qq plots, is more associated with the card rotation and paper folding tests, which measure visuospatial ability. This suggests that certain lineup tasks may require more visual ability than others; in this case, the qq-plot lineups required participants to mentally rotate plots, compare vertical distances, and perform more mental manipulation than the first two lineup tasks. }

>>>>

\newtext{Figure \ref{fig:lineuptaskmatrix} shows the correlations between the three lineup tasks and the figure classification, card rotation, and paper folding tasks. The visual search task was only slightly correlated with the three lineup tasks and has been omitted from this figure. Performance on lineup tasks 1 and 2, which dealt with the distributuion of two groups of numerical data, is most strongly correlated with the performance on the figure classification task, which measures general reasoning ability.}
\newtext{Performance on lineup task 3, which dealt with the identification of nonnormal residual qq plots, is more associated with the card rotation and paper folding tests, which measure visuospatial ability. This suggests that certain lineup tasks may require more visual ability than others; in this case, the qq-plot lineups required participants to mentally rotate plots, compare vertical distances, and perform more mental manipulation than the first two lineup tasks.}
